demographicvariablesregression

### 2023-02-10 combined data set/demovariablesregression.Rmd
mean to median in graphs

p1 <- sum_gender%>% 
  filter(Technology %in% c("Wind","Nuclear","Solar","Oil","Hydro","Gas","Coal")) %>%
  ggplot(aes(x=Technology, y= mean, fill = gender))+
  geom_bar(stat="identity", position=position_dodge())+
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.9)) +
  ylim(0,5)+
  scale_fill_manual(values=c("red", "blue"), name="legend")+
  labs(y = "Mean perceivd risk", x = "Energy Technologies")+
  ggtitle("Perceived risk and benefit from centrally owned energy technologies by gender")+
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))

p2 <- sum_gender%>% 
  filter(Technology %in% c("INDHydro", "INDSolar", "INDWind", "INDBiogas","INDDiesel", "INDKerosene","INDFirewoodetc","INDLPG")) %>%
  ggplot(aes(x=Technology, y= mean, fill = gender))+
  geom_bar(stat="identity", position=position_dodge())+
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.9)) +
  ylim(0,5)+
  scale_fill_manual(values=c("red", "blue"), name="legend")+
  labs(y = "Mean perceived risk", x = "Energy Technologies")+
  ggtitle("Perceived risk and benefit from individually owned energy technologies by gender")+
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))

@@

# conducting 
library(stats)

@@

library(dplyr)
library(purrr)

demovars %>% 
  filter(gender %in% c("Male", "Female"))%>%
  select(starts_with("Risky")) %>% 
  lapply(function(col) wilcox.test(col ~ gender, data = demovars))

>>>>

p1 <- sum_gender%>% 
  filter(Technology %in% c("Wind","Nuclear","Solar","Oil","Hydro","Gas","Coal")) %>%
  ggplot(aes(x=Technology, y= median, fill = gender))+
  geom_bar(stat="identity", position=position_dodge())+
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.9)) +
  ylim(0,5)+
  scale_fill_manual(values=c("red", "blue"), name="legend")+
  labs(y = "Median perceivd risk", x = "Energy Technologies")+
  ggtitle("Perceived risk and benefit from centrally owned energy technologies by gender")+
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))

p2 <- sum_gender%>% 
  filter(Technology %in% c("INDHydro", "INDSolar", "INDWind", "INDBiogas","INDDiesel", "INDKerosene","INDFirewoodetc","INDLPG")) %>%
  ggplot(aes(x=Technology, y= median, fill = gender))+
  geom_bar(stat="identity", position=position_dodge())+
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.9)) +
  ylim(0,5)+
  scale_fill_manual(values=c("red", "blue"), name="legend")+
  labs(y = "Median perceived risk", x = "Energy Technologies")+
  ggtitle("Perceived risk and benefit from individually owned energy technologies by gender")+
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))

@@

# conducting non-parametric procedure : "Wilcoxon rank-sum test" to see how perception of risk may differ according to gender. 
library(stats)
library(dplyr)
library(purrr)
library(broom)

@@

wilcox_gender <- demovars %>% 
  filter(gender %in% c("Male", "Female"))%>%
  select(starts_with("Risky")) %>% 
  lapply(function(col) wilcox.test(col ~ gender, data = demovars))

wilcox_gender <- do.call(rbind, wilcox_gender)

wilcox_gender

```
```{r}

# for making a data frame from wilcox test
#wilcox_gender <- demovars %>% 
  #filter(gender %in% c("Male", "Female"))%>%
  #select(starts_with("Risky")) %>% 
  #lapply(function(col) broom::tidy(wilcox.test(col ~ gender, data = demovars)))

#wilcox_gender <- do.call(rbind, wilcox_gender)

#wilcox_gender$variable <- rownames(wilcox_gender)

#wilcox_gender <- as.data.frame(wilcox_gender)
```
